### 2025-01-27 paper/appendix.qmd
waste of bloody time

- **Energy Penalty**: *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-moons-lambda_energy_exper", title="Results for Linearly Separable data by energy penalty.")
```

@@

::: {#tbl-moons-lambda_energy_exper}

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs)
```

Results for Moons data by energy penalty.

@@

::: {#tbl-circles-lambda_energy_exper}

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs)
```

@@

Results for Circles data by energy penalty.

>>>>

- **Energy Penalty** (@tbl-lin_sep-lambda_energy_exper): *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-lin_sep-lambda_energy_exper", title="Results for Linearly Separable data by energy penalty.")
```

@@

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-moons-lambda_energy_exper", title="Results for Moons data by energy penalty.")
```

@@

@@

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_energy_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; label="tbl-circles-lambda_energy_exper", title="Results for Circles data by energy penalty.")
```

@@

### 2025-01-27 paper/appendix.tex
waste of bloody time

---
format:
  latex:
    template: bare.tex
---

## Appendix

Here's my awesome appendix.

>>>>

\section{Appendix}\label{appendix}

\subsection{Initial Grid Search}\label{initial-grid-search}

\subsubsection{Generator Params}\label{generator-params}

\paragraph{Linearly Separable}\label{linearly-separable}

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-lin_sep-lambda_energy_exper}):
  \emph{ECCo} generally does yield better results than \emph{Vanilla}
  for higher choices of the energy penalty (10,15) during training.
  \emph{Generic} performs poorly accross the board. \emph{Omni} seems to
  have an anchoring effect, in that it never performs terribly but also
  never as good as the best \emph{ECCo} results. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost (distance penalty)}: Results for all generators (except
  \emph{Omni}) are quite bad, which can likely be attributed to
  extremely bad results for some choices of the \textbf{Energy Penalty}
  (results here are averaged). For \emph{ECCo} and \emph{Generic},
  higher cost values generally lead to worse results.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} almost always valid except for very low
  values during training and high values at evaluation time.
  \emph{Generic} often has poor validity.
\item
  \textbf{Accuracy}: Seems largely unaffected.
\end{itemize}

\begin{longtable}{ccccc}

\caption{\label{tbl-lin_sep-lambda_energy_exper}Results for Linearly Separable data by energy penalty.}

\tabularnewline

  \\
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & $-9.91 \cdot 10^{11}$ & $2.25 \cdot 10^{12}$ \\
  full & 0.01 & \textit{Generic} & $-5.71 \cdot 10^{17}$ & $1.3 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.54}} & \color{blue}{\textbf{0.116}} \\
  full & 0.01 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.01 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.01 & \textit{Generic} & -4.45 & 3.47 \\
  vanilla & 0.01 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 0.01 & \textit{REVISE} & -4.91 & 4.24 \\
  full & 0.05 & \textit{ECCo} & $-5.63 \cdot 10^{5}$ & $1.28 \cdot 10^{6}$ \\
  full & 0.05 & \textit{Generic} & $-8.35 \cdot 10^{17}$ & $1.9 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.53}} & \color{blue}{\textbf{0.114}} \\
  full & 0.05 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.05 & \textit{ECCo} & -4.4 & 3.66 \\
  vanilla & 0.05 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.05 & \textit{Omniscient} & -5.25 & 4.62 \\
  vanilla & 0.05 & \textit{REVISE} & -4.94 & 4.22 \\
  full & 0.1 & \textit{ECCo} & $-6.74 \cdot 10^{5}$ & $1.53 \cdot 10^{6}$ \\
  full & 0.1 & \textit{Generic} & $-1.72 \cdot 10^{11}$ & $3.9 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.56}} & \color{blue}{\textbf{0.124}} \\
  full & 0.1 & \textit{REVISE} & -15.6 & 13.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.28 & 3.52 \\
  vanilla & 0.1 & \textit{Generic} & -4.45 & 3.48 \\
  vanilla & 0.1 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 0.1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 0.5 & \textit{ECCo} & -11.8 & 9.83 \\
  full & 0.5 & \textit{Generic} & $-1.06 \cdot 10^{18}$ & $2.42 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.54}} & \color{blue}{\textbf{0.123}} \\
  full & 0.5 & \textit{REVISE} & -15 & 12.6 \\
  vanilla & 0.5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 0.5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 0.5 & \textit{Omniscient} & -5.25 & 4.61 \\
  vanilla & 0.5 & \textit{REVISE} & -4.95 & 4.22 \\
  full & 1 & \textit{ECCo} & -11.5 & 11.1 \\
  full & 1 & \textit{Generic} & $-1.71 \cdot 10^{11}$ & $3.88 \cdot 10^{11}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.59}} & \color{blue}{\textbf{0.117}} \\
  full & 1 & \textit{REVISE} & -15.7 & 13.3 \\
  vanilla & 1 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 1 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 1 & \textit{Omniscient} & -5.11 & 4.46 \\
  vanilla & 1 & \textit{REVISE} & -4.91 & 4.25 \\
  full & 5 & \textit{ECCo} & -3.99 & 3.12 \\
  full & 5 & \textit{Generic} & $-4.88 \cdot 10^{17}$ & $1.11 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.53}} & \color{blue}{\textbf{0.117}} \\
  full & 5 & \textit{REVISE} & -14.6 & 12.1 \\
  vanilla & 5 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 5 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 5 & \textit{Omniscient} & -5.25 & 4.61 \\
  vanilla & 5 & \textit{REVISE} & -4.95 & 4.22 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.31}} & \color{blue}{\textbf{0.735}} \\
  full & 10 & \textit{Generic} & $-1.7 \cdot 10^{11}$ & $3.86 \cdot 10^{11}$ \\
  full & 10 & \textit{Omniscient} & -2.53 & 0.117 \\
  full & 10 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 10 & \textit{ECCo} & -4.28 & 3.51 \\
  vanilla & 10 & \textit{Generic} & -4.44 & 3.47 \\
  vanilla & 10 & \textit{Omniscient} & -5.12 & 4.46 \\
  vanilla & 10 & \textit{REVISE} & -4.91 & 4.24 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.01}} & \color{blue}{\textbf{0.488}} \\
  full & 15 & \textit{Generic} & $-4.91 \cdot 10^{17}$ & $1.12 \cdot 10^{18}$ \\
  full & 15 & \textit{Omniscient} & -2.53 & 0.116 \\
  full & 15 & \textit{REVISE} & -14.4 & 11.7 \\
  vanilla & 15 & \textit{ECCo} & -4.4 & 3.65 \\
  vanilla & 15 & \textit{Generic} & -4.38 & 3.48 \\
  vanilla & 15 & \textit{Omniscient} & -5.25 & 4.6 \\
  vanilla & 15 & \textit{REVISE} & -4.95 & 4.23 \\\bottomrule

\end{longtable}

\paragraph{Moons}\label{moons}

\begin{longtable}{ccccc}

\caption{\label{tbl-moons-lambda_energy_exper}Results for Moons data by energy penalty.}

\tabularnewline

  \\
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0.01 & \textit{ECCo} & $-2.8 \cdot 10^{22}$ & $6.39 \cdot 10^{22}$ \\
  full & 0.01 & \textit{Generic} & $-4.89 \cdot 10^{30}$ & $1.11 \cdot 10^{31}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.74}} & \color{blue}{\textbf{5.08}} \\
  full & 0.01 & \textit{REVISE} & -572 & $1.25 \cdot 10^{3}$ \\
  vanilla & 0.01 & \textit{ECCo} & -15.5 & 17.3 \\
  vanilla & 0.01 & \textit{Generic} & -10.9 & 11.9 \\
  vanilla & 0.01 & \textit{Omniscient} & -12.7 & 14.4 \\
  vanilla & 0.01 & \textit{REVISE} & -11.2 & 13 \\
  full & 0.05 & \textit{ECCo} & $-1.55 \cdot 10^{16}$ & $3.52 \cdot 10^{16}$ \\
  full & 0.05 & \textit{Generic} & $-2.22 \cdot 10^{20}$ & $5 \cdot 10^{20}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.41}} & \color{blue}{\textbf{4.48}} \\
  full & 0.05 & \textit{REVISE} & $-1.04 \cdot 10^{3}$ & $2.3 \cdot 10^{3}$ \\
  vanilla & 0.05 & \textit{ECCo} & -15.5 & 17.2 \\
  vanilla & 0.05 & \textit{Generic} & -11.7 & 12.8 \\
  vanilla & 0.05 & \textit{Omniscient} & -12.4 & 14.1 \\
  vanilla & 0.05 & \textit{REVISE} & -11.3 & 13.1 \\
  full & 0.1 & \textit{ECCo} & $-3.41 \cdot 10^{3}$ & $7.73 \cdot 10^{3}$ \\
  full & 0.1 & \textit{Generic} & $-5.22 \cdot 10^{30}$ & $1.19 \cdot 10^{31}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.78}} & \color{blue}{\textbf{5.12}} \\
  full & 0.1 & \textit{REVISE} & -288 & 594 \\
  vanilla & 0.1 & \textit{ECCo} & -15.5 & 17.2 \\
  vanilla & 0.1 & \textit{Generic} & -10.9 & 11.9 \\
  vanilla & 0.1 & \textit{Omniscient} & -12.7 & 14.4 \\
  vanilla & 0.1 & \textit{REVISE} & -11.3 & 13.1 \\
  full & 0.5 & \textit{ECCo} & -7.09 & 7.51 \\
  full & 0.5 & \textit{Generic} & $-1.11 \cdot 10^{31}$ & $2.53 \cdot 10^{31}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.58}} & \color{blue}{\textbf{4.83}} \\
  full & 0.5 & \textit{REVISE} & $-1.19 \cdot 10^{3}$ & $2.64 \cdot 10^{3}$ \\
  vanilla & 0.5 & \textit{ECCo} & -15.5 & 17.2 \\
  vanilla & 0.5 & \textit{Generic} & -11.7 & 12.8 \\
  vanilla & 0.5 & \textit{Omniscient} & -12.4 & 14.1 \\
  vanilla & 0.5 & \textit{REVISE} & -11.3 & 13.1 \\
  full & 1 & \textit{ECCo} & -6.06 & 6.33 \\
  full & 1 & \textit{Generic} & $-1.58 \cdot 10^{33}$ & $3.59 \cdot 10^{33}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-4.66}} & \color{blue}{\textbf{4.89}} \\
  full & 1 & \textit{REVISE} & $-1.16 \cdot 10^{3}$ & $2.59 \cdot 10^{3}$ \\
  vanilla & 1 & \textit{ECCo} & -15.5 & 17.3 \\
  vanilla & 1 & \textit{Generic} & -10.9 & 11.9 \\
  vanilla & 1 & \textit{Omniscient} & -12.7 & 14.4 \\
  vanilla & 1 & \textit{REVISE} & -11.3 & 13.1 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-2.57}} & \color{blue}{\textbf{2.07}} \\
  full & 5 & \textit{Generic} & $-1.17 \cdot 10^{28}$ & $2.66 \cdot 10^{28}$ \\
  full & 5 & \textit{Omniscient} & -4.29 & 4.31 \\
  full & 5 & \textit{REVISE} & -530 & $1.16 \cdot 10^{3}$ \\
  vanilla & 5 & \textit{ECCo} & -15.5 & 17.2 \\
  vanilla & 5 & \textit{Generic} & -11.7 & 12.7 \\
  vanilla & 5 & \textit{Omniscient} & -12.4 & 14.1 \\
  vanilla & 5 & \textit{REVISE} & -11.3 & 13.1 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.76}} & \color{blue}{\textbf{0.974}} \\
  full & 10 & \textit{Generic} & $-1.54 \cdot 10^{33}$ & $3.51 \cdot 10^{33}$ \\
  full & 10 & \textit{Omniscient} & -4.44 & 4.56 \\
  full & 10 & \textit{REVISE} & $-1.52 \cdot 10^{3}$ & $3.4 \cdot 10^{3}$ \\
  vanilla & 10 & \textit{ECCo} & -15.5 & 17.3 \\
  vanilla & 10 & \textit{Generic} & -10.9 & 11.9 \\
  vanilla & 10 & \textit{Omniscient} & -12.7 & 14.4 \\
  vanilla & 10 & \textit{REVISE} & -11.3 & 13.1 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.37}} & \color{blue}{\textbf{0.365}} \\
  full & 15 & \textit{Generic} & $-5.32 \cdot 10^{28}$ & $1.21 \cdot 10^{29}$ \\
  full & 15 & \textit{Omniscient} & -4.34 & 4.38 \\
  full & 15 & \textit{REVISE} & -473 & $1.03 \cdot 10^{3}$ \\
  vanilla & 15 & \textit{ECCo} & -15.5 & 17.2 \\
  vanilla & 15 & \textit{Generic} & -11.7 & 12.8 \\
  vanilla & 15 & \textit{Omniscient} & -12.4 & 14.1 \\
  vanilla & 15 & \textit{REVISE} & -11.3 & 13.1 \\\bottomrule

\end{longtable}

\paragraph{Circles}\label{circles}

\begin{longtable}{ccccc}

\caption{\label{tbl-circles-lambda_energy_exper}Results for Circles data by energy penalty.}

\tabularnewline

  \\
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Obj.} & \textbf{\textbackslash{}lambda (exper)} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.01}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.26}} & \color{blue}{\textbf{0.423}} \\
  full & 0.01 & \textit{Generic} & -1.49 & 0.71 \\
  full & 0.01 & \textit{Omniscient} & -5.21 & 5.25 \\
  full & 0.01 & \textit{REVISE} & $-2.71 \cdot 10^{26}$ & $6.37 \cdot 10^{26}$ \\
  vanilla & 0.01 & \textit{ECCo} & -9.33 & 7.34 \\
  vanilla & 0.01 & \textit{Generic} & -8.89 & 6.88 \\
  vanilla & 0.01 & \textit{Omniscient} & -8.67 & 6.87 \\
  vanilla & 0.01 & \textit{REVISE} & -8.65 & 6.8 \\
  full & 0.05 & \textit{ECCo} & -1.29 & 0.397 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.05}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.21}} & \color{blue}{\textbf{0.356}} \\
  full & 0.05 & \textit{Omniscient} & -5.08 & 5.09 \\
  full & 0.05 & \textit{REVISE} & $-5.91 \cdot 10^{27}$ & $1.36 \cdot 10^{28}$ \\
  vanilla & 0.05 & \textit{ECCo} & -9.35 & 7.32 \\
  vanilla & 0.05 & \textit{Generic} & -8.85 & 6.87 \\
  vanilla & 0.05 & \textit{Omniscient} & -8.7 & 6.96 \\
  vanilla & 0.05 & \textit{REVISE} & -8.52 & 6.76 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.2}} & \color{blue}{\textbf{0.383}} \\
  full & 0.1 & \textit{Generic} & -1.5 & 0.735 \\
  full & 0.1 & \textit{Omniscient} & -5.17 & 5.23 \\
  full & 0.1 & \textit{REVISE} & $-3.06 \cdot 10^{26}$ & $7.7 \cdot 10^{26}$ \\
  vanilla & 0.1 & \textit{ECCo} & -9.33 & 7.32 \\
  vanilla & 0.1 & \textit{Generic} & -8.88 & 6.86 \\
  vanilla & 0.1 & \textit{Omniscient} & -8.69 & 6.9 \\
  vanilla & 0.1 & \textit{REVISE} & -8.68 & 6.81 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.5}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.12}} & \color{blue}{\textbf{0.217}} \\
  full & 0.5 & \textit{Generic} & -1.21 & 0.352 \\
  full & 0.5 & \textit{Omniscient} & -5.09 & 5.12 \\
  full & 0.5 & \textit{REVISE} & $-5.97 \cdot 10^{27}$ & $1.37 \cdot 10^{28}$ \\
  vanilla & 0.5 & \textit{ECCo} & -9.35 & 7.3 \\
  vanilla & 0.5 & \textit{Generic} & -8.89 & 6.92 \\
  vanilla & 0.5 & \textit{Omniscient} & -8.68 & 6.93 \\
  vanilla & 0.5 & \textit{REVISE} & -8.53 & 6.75 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{1}} & \color{blue}{\textbf{ECCo}} & \color{blue}{\textbf{-1.1}} & \color{blue}{\textbf{0.163}} \\
  full & 1 & \textit{Generic} & -1.49 & 0.726 \\
  full & 1 & \textit{Omniscient} & -5.16 & 5.2 \\
  full & 1 & \textit{REVISE} & $-3.09 \cdot 10^{26}$ & $7.22 \cdot 10^{26}$ \\
  vanilla & 1 & \textit{ECCo} & -9.34 & 7.36 \\
  vanilla & 1 & \textit{Generic} & -8.86 & 6.85 \\
  vanilla & 1 & \textit{Omniscient} & -8.7 & 6.9 \\
  vanilla & 1 & \textit{REVISE} & -8.69 & 6.85 \\
  full & 5 & \textit{ECCo} & -1.75 & 0.154 \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{5}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.21}} & \color{blue}{\textbf{0.363}} \\
  full & 5 & \textit{Omniscient} & -5.14 & 5.16 \\
  full & 5 & \textit{REVISE} & $-1.1 \cdot 10^{28}$ & $2.5 \cdot 10^{28}$ \\
  vanilla & 5 & \textit{ECCo} & -9.36 & 7.32 \\
  vanilla & 5 & \textit{Generic} & -8.88 & 6.91 \\
  vanilla & 5 & \textit{Omniscient} & -8.7 & 6.93 \\
  vanilla & 5 & \textit{REVISE} & -8.52 & 6.73 \\
  full & 10 & \textit{ECCo} & $-1.02 \cdot 10^{6}$ & $2.32 \cdot 10^{6}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{10}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.49}} & \color{blue}{\textbf{0.702}} \\
  full & 10 & \textit{Omniscient} & -5.13 & 5.16 \\
  full & 10 & \textit{REVISE} & $-3.74 \cdot 10^{26}$ & $9.09 \cdot 10^{26}$ \\
  vanilla & 10 & \textit{ECCo} & -9.31 & 7.33 \\
  vanilla & 10 & \textit{Generic} & -8.87 & 6.86 \\
  vanilla & 10 & \textit{Omniscient} & -8.7 & 6.89 \\
  vanilla & 10 & \textit{REVISE} & -8.69 & 6.83 \\
  full & 15 & \textit{ECCo} & $-3.31 \cdot 10^{13}$ & $7.54 \cdot 10^{13}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{15}} & \color{blue}{\textbf{Generic}} & \color{blue}{\textbf{-1.22}} & \color{blue}{\textbf{0.37}} \\
  full & 15 & \textit{Omniscient} & -5.2 & 5.23 \\
  full & 15 & \textit{REVISE} & $-9.01 \cdot 10^{27}$ & $2.06 \cdot 10^{28}$ \\
  vanilla & 15 & \textit{ECCo} & -9.38 & 7.34 \\
  vanilla & 15 & \textit{Generic} & -8.86 & 6.87 \\
  vanilla & 15 & \textit{Omniscient} & -8.69 & 6.96 \\
  vanilla & 15 & \textit{REVISE} & -8.51 & 6.73 \\\bottomrule

\end{longtable}
